Follow-up Samples

### 2017-02-20 submission/manuscript_outline_20161024.Rmd
title changes

# Differences in the fecal Microbiome Before and After Colorectal Cancer Treatment
```{r knitr_settings, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

\begin{center}
Running Title: Human Microbiome and Colorectal Cancer

>>>>

# The Fecal Microbiome Before and After Treatment for Colorectal Adenoma or Carcinoma
```{r knitr_settings, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

\begin{center}
Running Title: Human Microbiome before and after Colorectal Cancer

### 2017-02-20 submission/manuscript_outline_20161024.tex
title changes

\section{Differences in the fecal Microbiome Before and After Colorectal
Cancer
Treatment}\label{differences-in-the-fecal-microbiome-before-and-after-colorectal-cancer-treatment}

>>>>

\section{The Fecal Microbiome Before and After Treatment for Colorectal
Adenoma or
Carcinoma}\label{the-fecal-microbiome-before-and-after-treatment-for-colorectal-adenoma-or-carcinoma}
